Structuring College Access

### 2025-03-14 index.qmd
add rq1 tables

# Example directories
graphs_dir <- file.path(".", "results", "graphs")

@@

@@

>>>>

# Example directories
graphs_dir <- file.path(".", "results", "graphs")
tables_dir <- file.path(".", "results", "tables")

@@

insert_rq1_table <- function(metro) {
  table_df <- readRDS(file.path(tables_dir, str_c('rq1_table_', metro, '.rds')))
  table_df[is.na(table_df)] <- NA_real_

  group_headings <- unique(table_df$variable)
  nrows <- nrow(table_df) / length(group_headings)
  i <- 1

  k <- kbl(table_df %>% select(-variable), escape = F, col.names = c('', rep(c('Mean', 'SD', 'P25', 'P50', 'P75'), 3)))

  for (g in group_headings) {
    k <- k %>% pack_rows(g, i, i + nrows - 1, colnum = 1, label_row_css = '')
    i <- i + nrows
  }

  k %>% 
    add_header_above(header = c(' ' = 1, '1980' = 5, '2000' = 5, '2020' = 5))
}

@@

      # Add RQ1 table
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines(str_c("#### Racial/ethnic and socioeconomic characteristics of ", heading_text, " Geomarkets over time"))

      writeLines('<div class="table-wrapper freeze-pane">')
      writeLines(insert_rq1_table(m))
      writeLines('</div>')
      writeLines('<div class="footnote">Table Notes:<br>- Race/ethnicity categories not available in 1980 Census: Asian, non-Hispanic; Two+ races, non-Hispanic; NHPI, non-Hispanic; AIAN non-Hispanic<br>- Household income measured using 2024 CPI</div>')
